Cluster Analysis Experiments

### 2024-02-02 clustering_analysis.qmd
Disparity calculations

@@

>>>>

```{r}

final_data_full_cats_percent_5_clusters <- tar_read(final_data_full_cats_percent_5_clusters) |> as_tibble()

final_data_full_cats_percent_5_clusters |>
  group_by(cluster)|>
  count("practice_code")|>
  gt()
```

@@

```{r}
final_data_full_cats_percent_over45_5_clusters <- tar_read(final_data_full_cats_percent_over45_5_clusters) |> as_tibble()

final_data_full_cats_percent_over45_5_clusters |>
  group_by(cluster)|>
  count("practice_code")|>
  gt()
```
